Comparative study of Dask and Spark for neuroimaging pipelines\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Natural Sciences and Engineering Research Council}

### 2019-06-13 latex/paper.tex
Modified dataset and incrementation sections

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{times}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\usepackage[caption=false]{subfig}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

%%%%% MATERIAL AND METHODS %%%%%%
\section{Material and Methods}
%% Material
We compare Dask (\textbf{v1.1.4}) and Spark (\textbf{v2.4.0}) based on two metrics
their scheduling and their makespan performance. All scripts used to perform our
experiments are available at
\href{https://github.com/mathdugre/paper-big-data-engines}{https://github.com/mathdugre/paper-big-data-engines}.
For our experiments, we used Compute Canada Cloud where each instance has 8 cores,
30GB RAM, 10GB bandwidth and is dedicated.

%% Incrementation
\subsection{Incrementation}
As our first experiment to benchmark the frameworks we used a simple incrementation
pipeline (see Algorithm~\ref{alg:incrementation}). It loads chunks from the 75GB
BigBrain\cite{ds052:01} image, increment its value by 1 a determined number of time
and save the result to an NFS as a Nifti image. Incrementing the data reduce the
caching effect. This experiment allows us to study the behavior of the frameworks
when all input are processed independently; i.e.\ each task in the graph only depends
on the previous one (see~\ref{Figure fig:tg-inc}).

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{times}
\usepackage{siunitx}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\usepackage[caption=false]{subfig}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

%%%%% MATERIAL AND METHODS %%%%%%
\section{Material and Methods}

\subsection{Engines}
Spark v2.4.0 and Dask v1.1.4 was used for the experiments.

\textbf{PySpark.RDD \cite{spark-rdd}}

\textbf{Dask.bag \cite{dask-bag}}

\textbf{Dask.delayed \cite{dask-delayed}}

\textbf{Dask.futures \cite{dask-futures}}

\subsection{Dataset}
For the incrementation and histogram experiment the BigBrain~\cite{Amunts:13} is
used. It is a three-dimensional image of a brain scanned at \SI{40}{\micro\metre}.
The data set store the intensity of each voxel and their position. This results in a
75GB image. It is stored in 125 chunks in the minc~\cite{minc} format. To perform our
experiment we convert the chunks into the nifti format. Also, using sam~\cite{sam} we
combine the chunks and split them into 30, 125 and 750 chunks of equal size; 2.5GB,
0.6GB, and 0.1GB, respectively.

\subsection{Applications}

%% Incrementation
\subsubsection{\textbf{Incrementation}}
As our first experiment to benchmark the frameworks we used a simple incrementation
pipeline (see Algorithm~\ref{alg:incrementation}). It reads chunks from the BigBrain
image, increments the intensity value of each voxel by 1 for a specified amount of
iterations and write the result to an NFS as a Nifti image. Incrementing the data
reduce the caching effect. This experiment allows us to study the behavior of the
frameworks when all input are processed independently; i.e.\ each task in the graph
only depends on the previous one (see~\ref{Figure fig:tg-inc}).

@@

\subsubsection{Histogram}

\subsection{Experiment}

\subsection{Infrastructure}
All experiments were performed on Compute Canda Cloud.

%% Material
We compare Dask (\textbf{v1.1.4}) and Spark (\textbf{v2.4.0}) based on two metrics
their scheduling and their makespan performance. All scripts used to perform our
experiments are available at
\href{https://github.com/mathdugre/paper-big-data-engines}{https://github.com/mathdugre/paper-big-data-engines}.
For our experiments, we used Compute Canada Cloud where each instance has 8 cores,
30GB RAM, 10GB bandwidth and is dedicated.
